upwell_IDX

### 2020-04-23 upwell_IDX.Rmd
edit
update

save(wind_daily, file = "Data/wind_daily.RData") 
```

>>>>

library(openair)
wind_daily_speed <- timeAverage(wind_data, avg.time = "day")
save(wind_daily, file = "Data/wind_daily.RData")

#Convert Wind Speed and Wind Direction to u/v Wind Components 
# Then get the daily average and then convert it back?
# https://rdrr.io/github/retostauffer/Rfoehnix/man/ddff2uv.html
```
